Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex

\section{Reliability of \ac{SUPERCOP} results}

Although we believe the \ac{SUPERCOP} toolkit and results give good indication
of how fast the different candidate implementations are, we do have some
comments on it.

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no {\verb Update() }
function available for all implementations, and that \ac{SUPERCOP} only
measures speed of hashing full byte strings. This is also a hassle for a
programmer who wants to use the implementations in \ac{SUPERCOP}

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \ac{KAT}s supplied.

\paragraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computers measured by
\ac{SUPERCOP}.

\paragraph{Extra compiler flags}

We do not compile the candidate implementation with the exact same arguments
that is used in \ac{SUPERCOP}, most notably we append the -fPIC flag. This flag
creates \emph{position independent code}, in other words machine instruction
code that can execute properly regardless of where in memory it resides. This
will make one less register available on the x86 architecture. While we cannot
directly prove that this will affect performance of the implementations. We do
however suspect it. A person writing an optimization for \ac{SUPERCOP} will have
to balance his use of resources, among them registers, to achieve maximum speed.
The loss of one register will then give a performance penalty.

>>>>

\section{Reliability of SUPERCOP results}

Although we believe the \ac{SUPERCOP} toolkit and results give good indication
of how fast the different candidate implementations are, we do have some
general comments on the way it works and how it relates to our results.

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no {\verb Update() }
function available for all implementations, and that \ac{SUPERCOP} only
measures speed of hashing full byte strings. We are questioning if this
discriminates implementations which actually can do more of their processing on
a call to {\verb Update() }. This is also a hassle for a programmer who wants
to use the implementations found in \ac{SUPERCOP}

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \ac{KAT}s supplied or
implementations which fail completely as hash functions, see section
\ref{sec:choosen_implementations} for details on the JH implementation.

\paragraph{Extra compiler flags}
We do not compile the candidate implementation with the exact same arguments
that is used in \ac{SUPERCOP}, most notably we append the -fPIC flag. This flag
creates \emph{position independent code}, in other words machine instruction
code that can execute properly regardless of where in memory it resides. This
will make one less register available on the x86 architecture. While we cannot
directly prove that this will affect performance of the implementations. We do
however suspect it. A person writing an optimization for \ac{SUPERCOP} will have
to balance his use of resources, among them registers, to achieve maximum speed.
The loss of one register will then give a performance penalty.
